### 2015-07-31 conclusion.tex
Revisions and better overhead plot.
Typos.

We introduced Spack, a package manager in development at LLNL, that
provides truly {\it parameterized} builds.  Spack implements
a novel, recursive {\it spec} syntax that simplifies the process of working
with large software configuration spaces, and it builds software
so that it will run correctly, regardless of the environment.
We outlined a number of Spack's unique features, including
versioned virtual dependencies, and its novel {\it concretization}
process, which converts an abstract build DAG into a concrete,
buildable spec.

We showed through four use cases that Spack is already increasing
operational efficiency in production at LLNL.  We believe that the
software management techniques implemented in Spack are applicable
to a broad range of HPC facilities.
Spack is available online at http://github.com/scalability-llnl/spack.

>>>>

We introduced Spack, a package manager in development at LLNL, that
provides truly {\it parameterized} builds.  Spack implements
a novel, recursive {\it spec} syntax that simplifies the process of working
with large software configuration spaces, and it builds software
so that it will run correctly, regardless of the environment.
We outlined a number of Spack's unique features, including
versioned virtual dependencies, and its novel {\it concretization}
process, which converts an abstract build DAG into a concrete,
build-able spec.

We showed through four use cases that Spack is already increasing
operational efficiency in production at LLNL.  We believe that the
software management techniques implemented in Spack are applicable
to a broad range of HPC facilities.
Spack is available online at \url{http://github.com/scalability-llnl/spack}.

### 2015-07-31 implementation-concretization.tex
Typos.

Figure~\ref{fig:concretization-time} shows the running time of concretization vs.
package DAG size in nodes.  We generated this plot by running {\tt concretize}
on all of Spack's 245 packages. We tested on three LLNL cluster front-end nodes:
a 2.3Ghz Intel Haswell node and a 2.6 GHz Intel Sandy Bridge node on our Linux
clusters, and the 3.6 GHz IBM Power7 front-end node of a Blue Gene/Q system.
Each point is the average of 10 trials.  For all but the 10
largest packages, concretization takes less than 2 seconds on all machines.
For larger DAGs, we begin to see a quadratic trend, but even for 50 nodes or more, 
concretization takes less than 4 seconds on the Haswell machine and 9 seconds on the 
Power7.
%
We expect this performance from our greedy, fixed-point method, and
it is sufficient for the packages we have built so far.
Its running time is insignificant compared to the build time of
most packages, and it only executes
once per build. 
More generally, concretization is an instance of the constraint
satisfaction problem, which is NP-complete. While concretization could become
more costly, we do not expect to see packages with
thousands of dependencies in the near future. We do not expect
it to become a bottleneck, even if we use a full constraint solver.

>>>>

Figure~\ref{fig:concretization-time} shows the running time of concretization vs.
package DAG size in nodes.  We generated this plot by running {\tt concretize}
on all of Spack's 245 packages. We tested on three LLNL cluster front-end nodes:
a 2.3GHz Intel Haswell node and a 2.6 GHz Intel Sandy Bridge node on our Linux
clusters, and the 3.6 GHz IBM Power7 front-end node of a Blue Gene/Q system.
Each point is the average of 10 trials.  For all but the 10
largest packages, concretization takes less than 2 seconds on all machines.
For larger DAGs, we begin to see a quadratic trend, but even for 50 nodes or more, 
concretization takes less than 4 seconds on the Haswell machine and 9 seconds on the 
Power7.
%
We expect this performance from our greedy, fixed-point method, and
it is sufficient for the packages we have built so far.
Its running time is insignificant compared to the build time of
most packages, and it only executes
once per build. 
More generally, concretization is an instance of the constraint
satisfaction problem, which is NP-complete. While concretization could become
more costly, we do not expect to see packages with
thousands of dependencies in the near future. We do not expect
it to become a bottleneck, even if we use a full constraint solver.
